---
title: "Fieldwork Monitor: Dating Conjoint (Germany & Austria)"
subtitle: "Turnbull-Dugarte, Lopez Ortega & Wurthmann"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-summary: "Show code"
    theme: flatly
    self-contained: true
    fig-width: 10
    fig-height: 7
    page-layout: full
params:
  min_n_for_results: 100
knitr:
  opts_chunk:
    dev: "ragg_png"
execute:
  warning: false
  message: false
---

# 0. Setup

```{r setup}
library(tidyverse)
library(cregg)
library(ggdist)
library(gridExtra)
library(patchwork)
library(gt)
library(janitor)
library(lubridate)
library(scales)

set.seed(12345)
theme_set(theme_ggdist())

# Country configurations
countries <- list(
  germany = list(
    label = "Germany",
    file = "../data/germany_latest.csv",
    target_n = 1200, buffer_n = 1320,
    parties = c("AfD", "CDU/CSU", "SPD", "Grune", "FDP", "Die Linke"),
    far_right = "AfD",
    center_right = "CDU/CSU",
    rejection_hashtag = "#NiemalsAfD",
    col_party = c("AfD" = "#009EE0", "CDU/CSU" = "#000000", "SPD" = "#E3000F",
                  "Grune" = "#64A12D", "FDP" = "#FFED00", "Die Linke" = "#BE3075"),
    quotas = list(
      gender = tibble(level = c("Woman", "Man"), target_pct = c(50.6, 49.4)),
      education = tibble(level = c("Low", "Medium", "High"), target_pct = c(36.2, 30.2, 33.6)),
      age = tibble(level = c("18-29", "30-39", "40-49", "50-59", "60-74"),
                   target_pct = c(21.27, 17.65, 16.30, 19.94, 24.84))
    ),
    party_detect = list(
      "AfD" = "AfD", "CDU/CSU" = "CDU", "SPD" = "SPD",
      "Grune" = "GRUNE|GRÜNE|Grüne", "FDP" = "FDP", "Die Linke" = "Linke"
    ),
    resp_party_levels = c("CDU/CSU", "SPD", "Grune", "FDP", "AfD", "Die Linke", "BSW", "None"),
    education_map = list(
      "Low" = c("Kein Abschluss / Hauptschulabschluss / Volksschulabschluss"),
      "Medium" = c("Mittlere Reife / Realschulabschluss"),
      "High" = c("Fachhochschulreife", "Abitur / Allgemeine Hochschulreife",
                  "Hochschulabschluss (FH / Universität)")
    ),
    age_qid = "qid501",
    sex_id_qid = "qid398"
  ),
  austria = list(
    label = "Austria",
    file = "../data/austria_latest.csv",
    target_n = 1200, buffer_n = 1320,
    parties = c("FPO", "OVP", "SPO", "Grune", "NEOS", "KPO"),
    far_right = "FPO",
    center_right = "OVP",
    rejection_hashtag = "#NiemalsFPO",
    col_party = c("FPO" = "#005DA5", "OVP" = "#63C3D0", "SPO" = "#E3000F",
                  "Grune" = "#88B626", "NEOS" = "#E84188", "KPO" = "#CC0000"),
    quotas = list(
      gender = tibble(level = c("Woman", "Man"), target_pct = c(50.1, 49.9)),
      education = tibble(level = c("Low", "Medium", "High"), target_pct = c(22.6, 44.36, 33.04)),
      age = tibble(level = c("18-29", "30-39", "40-49", "50-59", "60-74"),
                   target_pct = c(21.10, 18.46, 17.51, 19.84, 23.09))
    ),
    party_detect = list(
      "FPO" = "FPÖ|FPO", "OVP" = "ÖVP|OVP", "SPO" = "SPÖ|SPO",
      "Grune" = "GRUNE|GRÜNE|Grüne", "NEOS" = "NEOS", "KPO" = "KPÖ|KPO"
    ),
    resp_party_levels = c("OVP", "SPO", "Grune", "NEOS", "FPO", "KPO", "None"),
    education_map = list(
      "Low" = c("Pflichtschulabschluss (Volksschule, Hauptschule, Polytechnikum)"),
      "Medium" = c("Lehre / BMS (Fachschule, Handelsschule)"),
      "High" = c("AHS / BHS mit Matura (HTL, HAK, HBLA)",
                  "Hochschulabschluss (FH / Universität)")
    ),
    age_qid = "qid499",
    sex_id_qid = "qid396"
  )
)

# Ethnicity map (same for both countries - based on face IDs)
ethnicity_map <- c(
  "W1" = "German", "W2" = "German", "W3" = "German", "W4" = "German",
  "W5" = "Other", "W6" = "German", "W7" = "Turkish",
  "W8" = "Other", "W9" = "German", "W10" = "Eastern European",
  "M1" = "German", "M2" = "Other", "M3" = "Turkish",
  "M4" = "Other", "M5" = "Other", "M6" = "German",
  "M7" = "German", "M8" = "German", "M9" = "German", "M10" = "Eastern European"
)

# Progressive cultural identity statements
progressive_statements <- c(
  "Ich schatze Vielfalt und setze mich fur Gleichstellung ein",
  "Gesellschaftlicher Wandel ist mir wichtig",
  "Ich setze mich fur eine gerechtere Welt ein",
  "Menschenrechte und Freiheit sind fur mich zentral",
  "Der Schutz von Umwelt und Klima ist mir ein Anliegen",
  "Ich engagiere mich fur Gleichberechtigung und gegen Diskriminierung",
  "Solidaritat ist ein wichtiger Teil meines Lebens",
  "Bildung und Kultur sollten allen offenstehen",
  "Ich befurworte eine offene und inklusive Gesellschaft",
  "Ich setze mich fur Frieden und Gewaltfreiheit ein",
  "Feminismus ist fur mich ein wichtiger Bezugspunkt",
  "Fur eine nachhaltige und okologische Zukunft",
  "Gegen soziale Ungleichheit, fur soziale Gerechtigkeit",
  "Liebe und gegenseitiger Respekt sind zentrale Werte",
  "Ich setze mich fur die Rechte von Arbeitnehmerinnen und Arbeitnehmern ein",
  "Ich befurworte mehr Beteiligung in der Demokratie",
  "Freiheit gilt nur, wenn sie fur alle gilt",
  "Meinungsfreiheit und kreative Entfaltung sind mir wichtig"
)
```


# 1. Data Loading & Processing

```{r load-process-data}
#| output: asis

process_country <- function(cfg, country_key) {
  # Load
  if (!file.exists(cfg$file)) {
    cat(paste0("**", cfg$label, ":** File not found: ", cfg$file, "\n\n"))
    return(NULL)
  }
  raw <- qualtRics::read_survey(cfg$file) |> clean_names()

  # Rename key variables (handle different QID numbers per country)
  age_col <- cfg$age_qid
  if (age_col %in% names(raw)) raw <- raw |> rename(age = !!sym(age_col))
  if ("duration_in_seconds" %in% names(raw)) {
    raw <- raw |> rename(duration_seconds = duration_in_seconds)
  }

  # Create sex_id from multi-select columns (varies by survey version)
  # Germany new: q62_1 through q62_8
  # Austria new: sexuality_id_1 through sexuality_id_8
  # Old surveys: single qid column
  sex_prefix <- if ("q62_1" %in% names(raw)) "q62" else if ("sexuality_id_1" %in% names(raw)) "sexuality_id" else NULL
  if (!is.null(sex_prefix)) {
    col1 <- paste0(sex_prefix, "_1")
    col2 <- paste0(sex_prefix, "_2")
    col3 <- paste0(sex_prefix, "_3")
    col4 <- paste0(sex_prefix, "_4")
    raw <- raw |> mutate(
      sex_id = case_when(
        !is.na(.data[[col1]]) ~ "Heterosexuell",
        !is.na(.data[[col2]]) ~ "Schwul/lesbisch",
        !is.na(.data[[col3]]) ~ "Bisexuell",
        !is.na(.data[[col4]]) ~ "Pansexuell",
        TRUE ~ NA_character_
      )
    )
  } else {
    sex_id_col <- cfg$sex_id_qid
    if (sex_id_col %in% names(raw)) raw <- raw |> rename(sex_id = !!sym(sex_id_col))
    if (!"sex_id" %in% names(raw)) raw$sex_id <- NA_character_
  }

  # Handle relationship_type multi-select (new surveys have relationship_type_1 through _5)
  if ("relationship_type_1" %in% names(raw) && !"relationship_type" %in% names(raw)) {
    raw <- raw |> mutate(
      relationship_type = case_when(
        !is.na(relationship_type_1) ~ relationship_type_1,
        !is.na(relationship_type_2) ~ relationship_type_2,
        !is.na(relationship_type_3) ~ relationship_type_3,
        !is.na(relationship_type_4) ~ relationship_type_4,
        !is.na(relationship_type_5) ~ relationship_type_5,
        TRUE ~ NA_character_
      )
    )
  }

  # Map sex_pref: handle both text labels and numeric
  if (is.character(raw$sex_pref)) {
    raw <- raw |> mutate(
      sex_pref = case_when(
        str_detect(sex_pref, "Nur M.nner") ~ 1,
        str_detect(sex_pref, "berwiegend M.nner") ~ 2,
        str_detect(sex_pref, "berwiegend Frauen") ~ 3,
        str_detect(sex_pref, "Nur Frauen") ~ 4,
        str_detect(sex_pref, "gleicherma") ~ 5,
        TRUE ~ NA_real_
      )
    )
  }

  # Filter
  n_raw <- nrow(raw)
  # Handle both logical and numeric finished
  if (is.logical(raw$finished)) {
    raw <- raw |> filter(finished == TRUE)
  } else {
    raw <- raw |> filter(finished == 1)
  }
  n_finished <- nrow(raw)

  # Handle both text and numeric consent
  if (is.character(raw$particip_agree)) {
    raw <- raw |> filter(str_detect(particip_agree, "stimme zu|Ich stimme"))
  } else {
    raw <- raw |> filter(particip_agree == 1)
  }
  n_consented <- nrow(raw)

  # --- Reshape attributes ---
  attributes_long <- raw |>
    select(response_id, starts_with("rd_")) |>
    mutate(across(starts_with("rd_"), as.character)) |>
    pivot_longer(cols = -response_id, names_to = "key", values_to = "value") |>
    separate(key, into = c("prefix", "round", "attribute"), sep = "_", extra = "merge") |>
    select(-prefix) |>
    mutate(round = as.character(round)) |>
    pivot_wider(names_from = attribute, values_from = value)

  # --- Extract decisions ---
  # QID numbers differ between Germany and Austria surveys
  # Germany: men=350-368, women=310-328
  # Austria: men=348-366, women=308-326
  if ("qid350" %in% names(raw)) {
    men_qids <- paste0("qid", seq(350, 368, by = 2))
    women_qids <- paste0("qid", seq(310, 328, by = 2))
  } else {
    men_qids <- paste0("qid", seq(348, 366, by = 2))
    women_qids <- paste0("qid", seq(308, 326, by = 2))
  }
  decision_map <- tibble(
    qid = c(men_qids, women_qids),
    arm_round = c(1:10, 1:10),
    arm = c(rep("mw", 10), rep("ww", 10))
  )

  available_qids <- intersect(decision_map$qid, names(raw))
  decision_map_avail <- decision_map |> filter(qid %in% available_qids)

  decisions_raw <- raw |>
    select(response_id, sex_pref, all_of(decision_map_avail$qid)) |>
    pivot_longer(cols = -c(response_id, sex_pref), names_to = "qid", values_to = "choice_text") |>
    left_join(decision_map_avail, by = "qid") |>
    filter(!is.na(choice_text) & choice_text != "")

  # Map text or numeric choices
  decisions <- decisions_raw |>
    mutate(
      choice = case_when(
        choice_text %in% c("Cancel", "1") ~ 1,
        choice_text %in% c("star", "2") ~ 2,
        choice_text %in% c("Heart", "4") ~ 4,
        TRUE ~ suppressWarnings(as.numeric(choice_text))
      ),
      round = case_when(
        sex_pref != 5 ~ as.character(arm_round),
        sex_pref == 5 & arm == "mw" ~ as.character(2 * arm_round - 1),
        sex_pref == 5 & arm == "ww" ~ as.character(2 * arm_round)
      )
    ) |>
    filter(!is.na(choice)) |>
    mutate(
      selected = ifelse(choice != 1, 1, 0),
      swipe = case_when(choice == 1 ~ "Reject", choice == 2 ~ "Super Like", choice == 4 ~ "Like")
    )

  # --- Merge ---
  conjoint <- decisions |>
    select(response_id, round, choice, selected, swipe, arm) |>
    inner_join(attributes_long, by = c("response_id", "round"))

  respondent_cols <- c("response_id", "gender", "sex_pref", "education_level",
                       "occupation", "age", "religion", "religiosity",
                       "party_id", "party_id_squeeze", "party_id_strength", "ideology_lr",
                       "political_interest", "tinder", "tinder_2",
                       "relationship_type", "relationship_now", "sex_id",
                       "duration_seconds", "start_date", "end_date", "ip_address")
  available_resp <- intersect(respondent_cols, names(raw))
  # Add bundesland/region if present
  if ("bundesland" %in% names(raw)) available_resp <- c(available_resp, "bundesland")

  respondent_vars <- raw |> select(all_of(available_resp))
  # Rename to avoid collision
  if ("gender" %in% names(respondent_vars)) {
    respondent_vars <- respondent_vars |> rename(resp_gender_raw = gender)
  }
  if ("age" %in% names(respondent_vars)) {
    respondent_vars <- respondent_vars |> rename(resp_age_raw = age)
  }
  if ("relationship_type" %in% names(respondent_vars)) {
    respondent_vars <- respondent_vars |> rename(resp_relationship_type = relationship_type)
  }

  conjoint <- conjoint |> left_join(respondent_vars, by = "response_id")

  # Drop missing engine data
  conjoint <- conjoint |>
    filter(!is.na(party_label), party_label != "",
           !is.na(person), person != "")

  # --- Recode party ---
  conjoint$PARTY <- NA_character_
  for (party_name in names(cfg$party_detect)) {
    pattern <- cfg$party_detect[[party_name]]
    if (party_name == cfg$far_right) {
      # Far-right: match only if no "Niemals" present
      idx <- which(is.na(conjoint$PARTY) &
                     str_detect(conjoint$party_label, pattern) &
                     !str_detect(conjoint$party_label, "Niemals|niemals"))
    } else {
      idx <- which(is.na(conjoint$PARTY) &
                     str_detect(conjoint$party_label, pattern))
    }
    if (length(idx) > 0) conjoint$PARTY[idx] <- party_name
  }

  conjoint <- conjoint |> mutate(
    REJECTION = case_when(
      str_detect(party_label, "Niemals|niemals") ~ "Anti-far-right signal",
      PARTY == cfg$far_right ~ paste0(cfg$far_right, " (no signal possible)"),
      TRUE ~ "No signal"
    ),
    REJECTION_BINARY = ifelse(str_detect(party_label, "Niemals|niemals"), 1, 0),
    REJECTION_CLEAN = factor(
      ifelse(REJECTION_BINARY == 1, "With rejection signal", "Without rejection signal"),
      levels = c("Without rejection signal", "With rejection signal")
    )
  )

  # --- Recode other attributes ---
  conjoint <- conjoint |> mutate(
    base_person = str_extract(person, "^[WM]\\d+"),
    variant_num = as.numeric(str_extract(person, "\\d+$")),
    FLAG = case_when(
      nationality == "" | is.na(nationality) ~ "No flag",
      str_detect(nationality, "german-european|austrian-european") ~ "National + EU flag",
      str_detect(nationality, "^german$|^austrian$") ~ "National flag",
      str_detect(nationality, "^european$") ~ "EU flag",
      TRUE ~ nationality
    ),
    BI = factor(ifelse(bisexual == TRUE | bisexual == "true" | bisexual == "TRUE",
                       "Bisexual", "Heterosexual"),
                levels = c("Heterosexual", "Bisexual")),
    TRANS = factor(ifelse(trans == TRUE | trans == "true" | trans == "TRUE",
                          "Trans", "Cis"),
                   levels = c("Cis", "Trans")),
    VEGAN = factor(ifelse(vegan != "" & !is.na(vegan) & vegan != "FALSE" & vegan != FALSE,
                          "Vegan", "Not vegan"),
                   levels = c("Not vegan", "Vegan")),
    CONGRUENCE = factor(
      ifelse(gender_congruence == "yes", "Gender congruent", "Non-congruent"),
      levels = c("Non-congruent", "Gender congruent")
    ),
    EMOTION = factor(
      ifelse(!is.na(emotion) & emotion != "",
             ifelse(str_detect(emotion, "smiling|Smiling"), "Smiling", "Neutral"),
             ifelse(variant_num %% 2 == 1, "Smiling", "Neutral")),
      levels = c("Neutral", "Smiling")
    ),
    DISTANCE = factor(case_when(
      str_detect(distance, "<1|weniger") ~ "<1km",
      str_detect(distance, "1-5|1 bis 5") ~ "1-5km",
      str_detect(distance, "5-10|5 bis 10") ~ "5-10km",
      str_detect(distance, ">10|mehr als 10") ~ ">10km",
      TRUE ~ NA_character_
    ), levels = c("<1km", "1-5km", "5-10km", ">10km")),
    ETHNICITY = factor(
      ifelse(!is.na(ethnicity) & ethnicity != "", ethnicity, ethnicity_map[base_person]),
      levels = c("German", "Turkish", "Eastern European", "Other")
    ),
    SOLIDARITY = case_when(
      international_solidarity == "" | is.na(international_solidarity) ~ "None",
      str_detect(international_solidarity, "FUCK TRUMP") ~ "Anti-Trump",
      str_detect(international_solidarity, "ProTRUMP") ~ "Pro-Trump",
      str_detect(international_solidarity, "ProPutin") ~ "Pro-Putin",
      str_detect(international_solidarity, "Ukraine") ~ "Pro-Ukraine",
      TRUE ~ international_solidarity
    ),
    RELATIONSHIP_SEEK = case_when(
      str_detect(relationship_type, "feste Partnerschaft") ~ "Committed",
      str_detect(relationship_type, "offene Beziehung") ~ "Open",
      str_detect(relationship_type, "unverbindliche") ~ "Casual",
      str_detect(relationship_type, "offen fur alles|offen für alles") ~ "Open to anything",
      str_detect(relationship_type, "Freundschaft") ~ "FWB",
      TRUE ~ "Unknown"
    ),
    CULTURAL_TYPE = factor(
      ifelse(cultural_identity %in% progressive_statements, "Progressive", "Conservative"),
      levels = c("Conservative", "Progressive")
    ),
    PROFILE_GENDER = factor(
      ifelse(str_detect(tolower(gender), "woman|frau"), "Woman", "Man"),
      levels = c("Woman", "Man")
    )
  )

  # Recode SES
  conjoint <- conjoint |> mutate(
    JOB_SLIM = case_when(
      job %in% c("Rechtsanwaltschaft/Jura", "Steuerberatung / Wirtschaftsprufung",
                 "Leitende Tatigkeit im Personalwesen", "Arztlich-medizinisches Personal",
                 "Bauingenieurwesen", "Webdesign", "Architekturburo",
                 "Wissenschaftliche Tatigkeit an einer Universitat",
                 "Softwareentwicklung", "Finanzanalyse",
                 "Hoherer offentlicher Dienst", "Leitung Unternehmensberatung",
                 "Steuerberatung / Wirtschaftsprüfung",
                 "Leitende Tätigkeit im Personalwesen", "Ärztlich-medizinisches Personal",
                 "Architekturbüro", "Wissenschaftliche Tätigkeit an einer Universität",
                 "Höherer öffentlicher Dienst") ~ "Upper professional",
      job %in% c("Pflegefachkraft", "Rettungsdienst", "IT-Fachkraft",
                 "Lehrkraft an einer weiterfuhrenden Schule",
                 "Lehrkraft an einer berufsbildenden Schule",
                 "Personliche Assistenz", "Lehrkraft an einer Grundschule",
                 "Lehrkraft an einer Volksschule",
                 "Laborfachkraft", "Polizei", "Grafikdesign",
                 "Offentlicher Dienst", "Finanzberatung",
                 "Filialleitung im Einzelhandel", "Fitnesscoach",
                 "Lehrkraft an einer weiterführenden Schule",
                 "Persönliche Assistenz", "Öffentlicher Dienst") ~ "Lower professional",
      job %in% c("Anstellung im Tatowierstudio", "Zahnmedizinische Assistenz",
                 "Fachkraft fur Elektrotechnik", "Buroassistenz",
                 "Pharmazeutische Assistenz", "Unterrichtsassistenz (padagogisch)",
                 "Maschinen- und Fahrzeugtechnik", "Abteilungsleitung im Einzelhandel",
                 "Assistenz im Personalwesen", "Immobilienvermittlung",
                 "Styling im Modebereich",
                 "Anstellung im Tätowierstudio", "Fachkraft für Elektrotechnik",
                 "Büroassistenz", "Unterrichtsassistenz (pädagogisch)") ~ "Skilled manual/service",
      job %in% c("Fachkraft im Einzelhandel", "Kassenmitarbeit im Einzelhandel",
                 "Anstellung im Bauwesen", "Lkw-Fahrdienst", "Kurierdienst",
                 "Reinigungspersonal", "Barservice", "Service im Restaurant",
                 "Callcenter-Tatigkeit", "Arbeit im Lagerbereich",
                 "Warenverraumung", "Taxifahrdienst",
                 "Callcenter-Tätigkeit", "Warenverräumung") ~ "Unskilled/routine",
      TRUE ~ "Unclassified"
    )
  )

  # --- Recode respondent variables ---
  conjoint <- conjoint |> mutate(
    resp_gender = factor(case_when(
      str_detect(resp_gender_raw, "Mann|mann") ~ "Man",
      str_detect(resp_gender_raw, "Frau|frau") ~ "Woman",
      str_detect(resp_gender_raw, "bin.r") ~ "Non-binary",
      resp_gender_raw == "1" ~ "Man",
      resp_gender_raw == "2" ~ "Woman",
      TRUE ~ NA_character_
    ), levels = c("Man", "Woman", "Non-binary")),
    resp_age = factor(case_when(
      str_detect(resp_age_raw, "18.29") ~ "18-29",
      str_detect(resp_age_raw, "30.39") ~ "30-39",
      str_detect(resp_age_raw, "40.49") ~ "40-49",
      str_detect(resp_age_raw, "50.59") ~ "50-59",
      str_detect(resp_age_raw, "60.74") ~ "60-74",
      resp_age_raw == "1" ~ "18-29",
      resp_age_raw == "2" ~ "30-39",
      resp_age_raw == "3" ~ "40-49",
      resp_age_raw == "4" ~ "50-59",
      resp_age_raw == "5" ~ "60-74",
      TRUE ~ NA_character_
    ), levels = c("18-29", "30-39", "40-49", "50-59", "60-74")),
    ideology_numeric = as.numeric(str_extract(as.character(ideology_lr), "^\\d+")),
    derecha = factor(case_when(
      ideology_numeric > 5 ~ "Right-wing",
      ideology_numeric < 5 ~ "Left-wing",
      TRUE ~ NA_character_
    ), levels = c("Left-wing", "Right-wing")),
    resp_farright = factor(ifelse(
      str_detect(party_id, cfg$far_right) | str_detect(coalesce(party_id_squeeze, ""), cfg$far_right),
      paste0(cfg$far_right, " supporter"),
      paste0("Not ", cfg$far_right, " supporter")
    )),
    resp_lgbtq = factor(case_when(
      is.na(sex_id) | sex_id == "" ~ NA_character_,
      sex_id %in% c("1", "Heterosexuell") ~ "Heterosexual",
      sex_id %in% c("Unsicher", "Keine Angabe") ~ NA_character_,
      TRUE ~ "LGBTQ+"
    ), levels = c("Heterosexual", "LGBTQ+"))
  )

  # Recode education for quota check
  conjoint <- conjoint |> mutate(
    resp_edu_level = case_when(
      as.character(education_level) %in% cfg$education_map[["Low"]] ~ "Low",
      as.character(education_level) %in% cfg$education_map[["Medium"]] ~ "Medium",
      as.character(education_level) %in% cfg$education_map[["High"]] ~ "High",
      # Numeric fallback
      education_level == "1" ~ "Low",
      education_level == "2" ~ "Medium",
      education_level %in% c("3", "4", "5") ~ "High",
      TRUE ~ NA_character_
    )
  )

  # Factor conversions
  conjoint <- conjoint |> mutate(
    PARTY = factor(PARTY, levels = names(cfg$party_detect)),
    FLAG = factor(FLAG, levels = c("No flag", "National flag", "National + EU flag", "EU flag")),
    SOLIDARITY = factor(SOLIDARITY, levels = c("None", "Anti-Trump", "Pro-Trump", "Pro-Putin", "Pro-Ukraine")),
    REJECTION = factor(REJECTION),
    RELATIONSHIP_SEEK = factor(RELATIONSHIP_SEEK),
    country = cfg$label
  )

  # Respondent-level data
  respondents <- conjoint |> distinct(response_id, .keep_all = TRUE)

  list(
    raw = raw,
    conjoint = conjoint,
    respondents = respondents,
    n_raw = n_raw,
    n_finished = n_finished,
    n_consented = n_consented,
    cfg = cfg
  )
}

# Process both countries
data <- list()
for (ck in names(countries)) {
  result <- tryCatch(
    process_country(countries[[ck]], ck),
    error = function(e) {
      cat(paste0("**Error processing ", countries[[ck]]$label, ":** ", e$message, "\n\n"))
      NULL
    }
  )
  if (!is.null(result)) data[[ck]] <- result
}

# Summary
for (ck in names(data)) {
  d <- data[[ck]]
  cat(paste0("**", d$cfg$label, ":** ",
             nrow(d$respondents), " respondents, ",
             nrow(d$conjoint), " profile evaluations\n\n"))
}
```


# 2. Collection Progress

```{r collection-progress, fig.height=5}
progress_data <- map_dfr(names(data), function(ck) {
  d <- data[[ck]]
  d$respondents |>
    mutate(
      date = as.Date(start_date),
      country = d$cfg$label,
      target = d$cfg$target_n
    ) |>
    select(response_id, date, country, target)
})

if (nrow(progress_data) > 0) {
  # Daily cumulative curve
  daily <- progress_data |>
    count(country, date, name = "daily_n") |>
    group_by(country) |>
    arrange(date) |>
    mutate(cumulative = cumsum(daily_n)) |>
    ungroup()

  targets <- progress_data |> distinct(country, target)

  ggplot(daily, aes(x = date, y = cumulative, color = country)) +
    geom_step(linewidth = 1.2) +
    geom_point(size = 2) +
    geom_hline(data = targets, aes(yintercept = target, color = country),
               linetype = "dashed", alpha = 0.5) +
    scale_y_continuous(labels = comma) +
    scale_color_manual(values = c("Germany" = "#DD1100", "Austria" = "#EE3333")) +
    labs(title = "Data Collection Progress",
         subtitle = "Dashed lines = target N (1,200 per country)",
         x = "Date", y = "Cumulative Respondents", color = NULL) +
    theme(plot.title = element_text(face = "bold"), legend.position = "bottom")

  # Progress table
  progress_tbl <- map_dfr(names(data), function(ck) {
    d <- data[[ck]]
    n <- nrow(d$respondents)
    tibble(
      Country = d$cfg$label,
      N = n,
      Target = d$cfg$target_n,
      `%` = round(n / d$cfg$target_n * 100, 1),
      `First response` = as.character(min(as.Date(d$respondents$start_date), na.rm = TRUE)),
      `Last response` = as.character(max(as.Date(d$respondents$start_date), na.rm = TRUE))
    )
  })

  progress_tbl |>
    gt() |>
    tab_header(title = "Collection Status") |>
    tab_style(style = cell_fill(color = "#d4edda"),
              locations = cells_body(rows = `%` >= 80)) |>
    tab_style(style = cell_fill(color = "#fff3cd"),
              locations = cells_body(rows = `%` >= 50 & `%` < 80)) |>
    tab_style(style = cell_fill(color = "#f8d7da"),
              locations = cells_body(rows = `%` < 50))
}
```


# 3. Quota Tracking {.tabset}

```{r quota-check-fn}
check_quotas <- function(d) {
  cfg <- d$cfg
  resp <- d$respondents
  n <- nrow(resp)

  results <- list()

  # Gender
  gender_obs <- resp |>
    count(resp_gender) |>
    mutate(observed_pct = round(n / sum(n) * 100, 1)) |>
    rename(level = resp_gender) |>
    mutate(level = as.character(level))
  gender_check <- cfg$quotas$gender |>
    left_join(gender_obs, by = "level") |>
    mutate(deviation = observed_pct - target_pct,
           dimension = "Gender")
  results$gender <- gender_check

  # Age
  age_obs <- resp |>
    count(resp_age) |>
    mutate(observed_pct = round(n / sum(n) * 100, 1)) |>
    rename(level = resp_age) |>
    mutate(level = as.character(level))
  age_check <- cfg$quotas$age |>
    left_join(age_obs, by = "level") |>
    mutate(deviation = observed_pct - target_pct,
           dimension = "Age")
  results$age <- age_check

  # Education
  edu_obs <- resp |>
    count(resp_edu_level) |>
    mutate(observed_pct = round(n / sum(n) * 100, 1)) |>
    rename(level = resp_edu_level) |>
    mutate(level = as.character(level))
  edu_check <- cfg$quotas$education |>
    left_join(edu_obs, by = "level") |>
    mutate(deviation = observed_pct - target_pct,
           dimension = "Education")
  results$education <- edu_check

  bind_rows(results)
}
```

```{r quota-plot-fn}
plot_quotas <- function(d) {
  quota_results <- check_quotas(d)
  quota_results |>
    mutate(label = paste0(dimension, ": ", level)) |>
    ggplot(aes(x = label)) +
    geom_col(aes(y = observed_pct), fill = "steelblue", alpha = 0.7, width = 0.6) +
    geom_point(aes(y = target_pct), color = "red", size = 3, shape = 18) +
    coord_flip() +
    facet_wrap(~dimension, scales = "free_y", ncol = 1) +
    labs(title = paste0(d$cfg$label, ": Observed vs Target Quotas"),
         subtitle = "Blue bars = observed, Red diamonds = target",
         x = NULL, y = "Percentage") +
    theme(plot.title = element_text(face = "bold"),
          strip.text = element_blank())
}
```

::: {.panel-tabset}

## Germany

```{r quota-germany, fig.height=6}
if ("germany" %in% names(data)) {
  plot_quotas(data[["germany"]])
  check_quotas(data[["germany"]]) |>
    gt() |> tab_header(title = "Germany: Quota Compliance")
}
```

## Austria

```{r quota-austria, fig.height=6}
if ("austria" %in% names(data)) {
  plot_quotas(data[["austria"]])
  check_quotas(data[["austria"]]) |>
    gt() |> tab_header(title = "Austria: Quota Compliance")
}
```

:::


# 4. Randomization Diagnostics {.tabset}

```{r rand-helpers}
calc_binomial_ci <- function(x, n, expected) {
  test <- binom.test(x, n, p = expected)
  tibble(
    observed_pct = round(x / n * 100, 1),
    expected_pct = expected * 100,
    deviation = round(observed_pct - expected_pct, 1),
    ci_lower = round(test$conf.int[1] * 100, 1),
    ci_upper = round(test$conf.int[2] * 100, 1),
    p_value = round(test$p.value, 3)
  )
}

safe_chisq <- function(var1, var2) {
  tbl <- table(var1, var2)
  tbl <- tbl[rowSums(tbl) > 0, colSums(tbl) > 0, drop = FALSE]
  if (min(dim(tbl)) < 2) return(NA_real_)
  tryCatch(
    chisq.test(tbl, simulate.p.value = TRUE, B = 2000)$p.value,
    error = function(e) NA_real_
  )
}

run_randomization_checks <- function(d) {
  conjoint <- d$conjoint
  cfg <- d$cfg
  n_profiles <- nrow(conjoint)
  cat(paste0("\n### ", cfg$label, " (N=", nrow(d$respondents),
             " respondents, ", n_profiles, " profiles)\n\n"))

  # --- Party distribution ---
  cat("#### Party Distribution\n\n")
  party_dist <- conjoint |>
    filter(!is.na(PARTY)) |>
    count(PARTY) |>
    mutate(observed_pct = round(n / sum(n) * 100, 1),
           expected_pct = round(100 / length(cfg$parties), 1),
           deviation = observed_pct - expected_pct)

  n_parties <- length(cfg$parties)
  party_chisq <- chisq.test(party_dist$n, p = rep(1/n_parties, n_parties))
  cat(paste0("Chi-squared: X2=", round(party_chisq$statistic, 2),
             ", p=", round(party_chisq$p.value, 3), "\n\n"))

  print(knitr::kable(party_dist, caption = paste0("Expected: ~", round(100/n_parties, 1), "% each")))
  cat("\n\n")

  # --- Rejection signal ---
  cat("#### Rejection Signal Rate\n\n")
  non_fr <- conjoint |> filter(PARTY != cfg$far_right)
  rej_rate <- mean(non_fr$REJECTION_BINARY, na.rm = TRUE)
  rej_test <- binom.test(sum(non_fr$REJECTION_BINARY), nrow(non_fr), p = 0.3)
  cat(paste0("Observed rejection rate (non-far-right): **",
             round(rej_rate * 100, 1), "%** (expected: 30%)\n\n"))
  cat(paste0("Binomial test: p=", round(rej_test$p.value, 3),
             ", 95% CI: [", round(rej_test$conf.int[1]*100, 1),
             "%, ", round(rej_test$conf.int[2]*100, 1), "%]\n\n"))

  fr_with_signal <- conjoint |> filter(PARTY == cfg$far_right & REJECTION_BINARY == 1)
  cat(paste0(cfg$far_right, " profiles with rejection signal (should be 0): ",
             nrow(fr_with_signal), "\n\n"))

  # --- Binary attributes ---
  cat("#### Binary Attributes\n\n")
  binary_checks <- bind_rows(
    calc_binomial_ci(sum(conjoint$BI == "Bisexual", na.rm = TRUE), n_profiles, 0.25) |>
      mutate(Attribute = "Bisexual (exp: 25%)"),
    calc_binomial_ci(sum(conjoint$TRANS == "Trans", na.rm = TRUE), n_profiles, 0.10) |>
      mutate(Attribute = "Trans (exp: 10%)"),
    calc_binomial_ci(sum(conjoint$VEGAN == "Vegan", na.rm = TRUE), n_profiles, 0.30) |>
      mutate(Attribute = "Vegan (exp: 30%)")
  ) |> select(Attribute, observed_pct, expected_pct, deviation, ci_lower, ci_upper, p_value)
  print(knitr::kable(binary_checks))
  cat("\n\n")

  # --- Categorical attributes ---
  cat("#### Categorical Attributes\n\n")

  cat("**Distance** (expected: 25% each)\n\n")
  print(knitr::kable(conjoint |> count(DISTANCE) |>
    mutate(pct = round(n/sum(n)*100, 1), expected = 25.0, dev = round(pct - expected, 1))))
  cat("\n")

  cat("**Relationship Type** (expected: 40/20/20/10/10)\n\n")
  print(knitr::kable(conjoint |> count(RELATIONSHIP_SEEK) |>
    mutate(pct = round(n/sum(n)*100, 1))))
  cat("\n")

  cat("**Nationality Flag** (expected: 25% each)\n\n")
  print(knitr::kable(conjoint |> count(FLAG) |>
    mutate(pct = round(n/sum(n)*100, 1))))
  cat("\n")

  cat("**Ethnicity**\n\n")
  print(knitr::kable(conjoint |> count(ETHNICITY) |>
    mutate(pct = round(n/sum(n)*100, 1))))
  cat("\n")

  cat("**Cultural Identity Type** (expected: ~53% conservative, ~47% progressive)\n\n")
  print(knitr::kable(conjoint |> count(CULTURAL_TYPE) |>
    mutate(pct = round(n/sum(n)*100, 1))))
  cat("\n\n")

  # --- Face deduplication ---
  cat("#### Face Deduplication\n\n")
  face_check <- conjoint |>
    group_by(response_id) |>
    summarise(n_profiles = n(), n_unique = n_distinct(person),
              has_repeat = n_profiles > n_unique, .groups = "drop")
  cat(paste0("Respondents with repeated faces: **", sum(face_check$has_repeat), "**\n\n"))

  # --- Age matching ---
  cat("#### Age Matching\n\n")
  age_check <- conjoint |>
    mutate(
      profile_age = suppressWarnings(as.numeric(age)),
      profile_bracket = case_when(
        profile_age >= 18 & profile_age <= 29 ~ "18-29",
        profile_age >= 30 & profile_age <= 49 ~ "30-49",
        profile_age >= 50 ~ "50-74",
        TRUE ~ NA_character_
      ),
      resp_bracket = case_when(
        resp_age %in% c("18-29") ~ "18-29",
        resp_age %in% c("30-39", "40-49") ~ "30-49",
        resp_age %in% c("50-59", "60-74") ~ "50-74"
      ),
      age_match = profile_bracket == resp_bracket
    )
  match_rate <- mean(age_check$age_match, na.rm = TRUE)
  cat(paste0("Age match rate: **", round(match_rate * 100, 1), "%** (expected: ~80-90%)\n\n"))

  # --- Cross-attribute independence ---
  cat("#### Cross-Attribute Independence\n\n")
  independence <- tibble(
    Pair = c("PARTY x BI", "PARTY x TRANS", "PARTY x VEGAN",
             "PARTY x DISTANCE", "PARTY x FLAG", "BI x TRANS"),
    p_value = c(
      safe_chisq(conjoint$PARTY, conjoint$BI),
      safe_chisq(conjoint$PARTY, conjoint$TRANS),
      safe_chisq(conjoint$PARTY, conjoint$VEGAN),
      safe_chisq(conjoint$PARTY, conjoint$DISTANCE),
      safe_chisq(conjoint$PARTY, conjoint$FLAG),
      safe_chisq(conjoint$BI, conjoint$TRANS)
    )
  ) |> mutate(
    p_value = round(p_value, 3),
    Status = ifelse(is.na(p_value), "N/A", ifelse(p_value > 0.05, "OK", "CONCERN"))
  )
  print(knitr::kable(independence))
  cat("\n\n")
}
```

::: {.panel-tabset}

## Germany

```{r rand-germany, results='asis'}
if ("germany" %in% names(data)) {
  run_randomization_checks(data[["germany"]])
}
```

## Austria

```{r rand-austria, results='asis'}
if ("austria" %in% names(data)) {
  run_randomization_checks(data[["austria"]])
}
```

:::


# 5. Data Quality {.tabset}

```{r quality-helpers}
quality_text <- function(d) {
  # Duration stats
  durations <- d$respondents |>
    mutate(duration_min = as.numeric(duration_seconds) / 60) |>
    filter(!is.na(duration_min))

  if (nrow(durations) > 0) {
    cat("#### Completion Times\n\n")
    cat(paste0("Median: ", round(median(durations$duration_min), 1), " min\n\n"))
    cat(paste0("Mean: ", round(mean(durations$duration_min), 1), " min\n\n"))
    n_speeders <- sum(durations$duration_min < 5)
    cat(paste0("Speeders (<5 min): **", n_speeders, "** (",
               round(n_speeders/nrow(durations)*100, 1), "%)\n\n"))
    n_slow <- sum(durations$duration_min > 60)
    cat(paste0("Very slow (>60 min): ", n_slow, "\n\n"))
  }

  # Attrition by round
  cat("#### Attrition by Round\n\n")
  round_counts <- d$conjoint |>
    count(round) |>
    mutate(round = as.numeric(round)) |>
    arrange(round)
  if (nrow(round_counts) > 0) {
    cat(paste0("Round 1: ", round_counts$n[1],
               " | Round 10: ", round_counts$n[nrow(round_counts)],
               " | Attrition: ",
               round((1 - round_counts$n[nrow(round_counts)] / round_counts$n[1]) * 100, 1),
               "%\n\n"))
  }

  # Duplicate IPs
  cat("#### Duplicate IPs\n\n")
  if ("ip_address" %in% names(d$respondents)) {
    dup_ips <- d$respondents |>
      count(ip_address) |>
      filter(n > 1)
    cat(paste0("Duplicate IPs: ", nrow(dup_ips), "\n\n"))
  } else {
    cat("IP address not available\n\n")
  }
}

quality_plots <- function(d) {
  # Duration histogram
  durations <- d$respondents |>
    mutate(duration_min = as.numeric(duration_seconds) / 60) |>
    filter(!is.na(duration_min))

  if (nrow(durations) > 0) {
    # Cap at 60 min for readability (outliers noted in subtitle)
    n_outliers <- sum(durations$duration_min > 60)
    p1 <- durations |>
      filter(duration_min <= 60) |>
      ggplot(aes(x = duration_min)) +
      geom_histogram(binwidth = 1, fill = "steelblue", color = "white", alpha = 0.8) +
      geom_vline(xintercept = 5, color = "red", linetype = "dashed") +
      labs(title = paste0(d$cfg$label, ": Completion Time Distribution"),
           subtitle = if (n_outliers > 0) paste0(n_outliers, " respondents >60 min not shown") else NULL,
           x = "Duration (minutes)", y = "Count") +
      theme(plot.title = element_text(face = "bold"))
    print(p1)
  }

  # Acceptance rate by round
  round_accept <- d$conjoint |>
    mutate(round_num = as.numeric(round)) |>
    group_by(round_num) |>
    summarise(accept_rate = mean(selected, na.rm = TRUE), .groups = "drop")
  if (nrow(round_accept) > 0) {
    p2 <- round_accept |>
      ggplot(aes(x = round_num, y = accept_rate)) +
      geom_line(color = "steelblue", linewidth = 1) +
      geom_point(color = "steelblue", size = 3) +
      geom_hline(yintercept = mean(d$conjoint$selected, na.rm = TRUE),
                 linetype = "dashed", alpha = 0.5) +
      scale_x_continuous(breaks = 1:10) +
      scale_y_continuous(labels = percent, limits = c(0, 1)) +
      labs(title = paste0(d$cfg$label, ": Acceptance Rate by Round"),
           subtitle = "Dashed line = overall mean",
           x = "Round", y = "Acceptance Rate") +
      theme(plot.title = element_text(face = "bold"))
    print(p2)
  }
}
```

::: {.panel-tabset}

## Germany

```{r quality-germany-text, results='asis'}
if ("germany" %in% names(data)) { quality_text(data[["germany"]]) }
```

```{r quality-germany-plots, fig.height=8}
if ("germany" %in% names(data)) { quality_plots(data[["germany"]]) }
```

## Austria

```{r quality-austria-text, results='asis'}
if ("austria" %in% names(data)) { quality_text(data[["austria"]]) }
```

```{r quality-austria-plots, fig.height=8}
if ("austria" %in% names(data)) { quality_plots(data[["austria"]]) }
```

:::


# 6. Preliminary Results

```{r results-gate}
show_results <- any(sapply(data, function(d) nrow(d$respondents) >= params$min_n_for_results))
min_n <- params$min_n_for_results
```

```{r results-message, eval=!show_results, results='asis'}
cat(paste0("\n**Preliminary results will appear when at least one country reaches N >= ",
           min_n, " respondents.**\n\n"))
cat("Current counts:\n\n")
for (ck in names(data)) {
  d <- data[[ck]]
  cat(paste0("- ", d$cfg$label, ": ", nrow(d$respondents), " / ", min_n, "\n"))
}
```

```{r results-helpers-v2}
# --- Multi-CI helper ---
add_multi_ci <- function(df) {
  df |> mutate(
    lower90  = estimate - 1.645 * std.error,
    higher90 = estimate + 1.645 * std.error,
    lower95  = estimate - 1.96 * std.error,
    higher95 = estimate + 1.96 * std.error,
    lower99  = estimate - 2.58 * std.error,
    higher99 = estimate + 2.58 * std.error
  )
}

# --- Feature labels ---
feature_labels <- c(
  "PARTY" = "Party", "BI" = "Sexual orientation", "TRANS" = "Gender identity",
  "VEGAN" = "Diet", "ETHNICITY" = "Ethnicity", "FLAG" = "Nationality flag",
  "SOLIDARITY" = "Int'l solidarity", "DISTANCE" = "Distance",
  "RELATIONSHIP_SEEK" = "Relationship type", "CONGRUENCE" = "Gender congruence",
  "EMOTION" = "Facial expression", "CULTURAL_TYPE" = "Cultural identity",
  "JOB_SLIM" = "Occupation", "REJECTION_CLEAN" = "Rejection signal"
)

# --- Core multi-CI plot ---
plot_multi_ci <- function(df, h0 = 0.5, title = "", subtitle = "",
                          xlimits = NULL, show_labels = FALSE, show_facets = FALSE,
                          color_var = NULL, color_vals = NULL) {
  df <- add_multi_ci(df)

  # Clean feature labels
  if ("feature" %in% names(df)) {
    df <- df |> mutate(
      feature = ifelse(feature %in% names(feature_labels), feature_labels[feature], feature),
      feature = factor(feature, levels = unique(feature))
    )
  }

  if (!is.null(color_var) && color_var %in% names(df)) {
    # Two-group overlay with nudge
    groups <- unique(df[[color_var]])
    g1 <- df |> filter(.data[[color_var]] == groups[1])
    g2 <- df |> filter(.data[[color_var]] == groups[2])

    p <- ggplot() +
      geom_vline(xintercept = h0, linetype = "dashed", alpha = 0.4) +
      # Group 1 (nudged up)
      geom_segment(data = g1, aes(x = lower99, xend = higher99, y = level, yend = level),
                   color = color_vals[1], size = 2, alpha = .6, position = position_nudge(y = .15)) +
      geom_segment(data = g1, aes(x = lower95, xend = higher95, y = level, yend = level),
                   color = color_vals[1], size = 3, alpha = .8, position = position_nudge(y = .15)) +
      geom_segment(data = g1, aes(x = lower90, xend = higher90, y = level, yend = level),
                   color = color_vals[1], size = 4, alpha = 1, position = position_nudge(y = .15)) +
      geom_point(data = g1, aes(x = estimate, y = level), fill = "white", color = color_vals[1],
                 size = 2.5, pch = 21, position = position_nudge(y = .15)) +
      # Group 2 (nudged down)
      geom_segment(data = g2, aes(x = lower99, xend = higher99, y = level, yend = level),
                   color = color_vals[2], size = 2, alpha = .6, position = position_nudge(y = -.15)) +
      geom_segment(data = g2, aes(x = lower95, xend = higher95, y = level, yend = level),
                   color = color_vals[2], size = 3, alpha = .8, position = position_nudge(y = -.15)) +
      geom_segment(data = g2, aes(x = lower90, xend = higher90, y = level, yend = level),
                   color = color_vals[2], size = 4, alpha = 1, position = position_nudge(y = -.15)) +
      geom_point(data = g2, aes(x = estimate, y = level), fill = "white", color = color_vals[2],
                 size = 2.5, pch = 21, position = position_nudge(y = -.15))

    # Manual legend
    p <- p + annotate("text", x = -Inf, y = Inf, label = paste0(groups[1], " / ", groups[2]),
                       hjust = -0.1, vjust = 1.5, size = 3.5, fontface = "italic",
                       color = "grey40")
  } else {
    p <- ggplot(df, aes(y = level)) +
      geom_vline(xintercept = h0, linetype = "dashed", alpha = 0.4) +
      geom_segment(aes(x = lower99, xend = higher99, y = level, yend = level),
                   color = "steelblue", size = 2, alpha = .6) +
      geom_segment(aes(x = lower95, xend = higher95, y = level, yend = level),
                   color = "steelblue", size = 3, alpha = .8) +
      geom_segment(aes(x = lower90, xend = higher90, y = level, yend = level),
                   color = "steelblue", size = 4, alpha = 1) +
      geom_point(aes(x = estimate, y = level), fill = "white", color = "grey67",
                 size = 2.5, pch = 21)
  }

  if (show_labels) {
    p <- p + geom_label(data = df, aes(x = estimate, y = level,
                         label = sprintf("%0.2f", estimate)),
                         nudge_y = .25, size = 3, fontface = "bold", alpha = 0.8)
  }

  if (show_facets && "feature" %in% names(df)) {
    p <- p + facet_grid(feature ~ ., scales = "free_y", space = "free_y")
  }

  p <- p +
    labs(title = title, subtitle = subtitle, x = NULL, y = NULL) +
    theme(plot.title = element_text(face = "bold", size = 11),
          plot.subtitle = element_text(size = 9),
          strip.text.y = element_text(angle = 0, hjust = 0, face = "bold"),
          strip.background = element_rect(fill = "grey95"),
          legend.position = "none")

  if (!is.null(xlimits)) p <- p + xlim(xlimits)

  p
}

# --- Full attribute formula ---
full_attr_formula <- function() {
  selected ~ PARTY + BI + TRANS + VEGAN + ETHNICITY + FLAG +
    SOLIDARITY + DISTANCE + RELATIONSHIP_SEEK + CONGRUENCE + EMOTION + CULTURAL_TYPE
}

# --- Full attribute overview ---
plot_full_attributes <- function(d) {
  conjoint <- d$conjoint
  cfg <- d$cfg

  mm_full <- mm(conjoint, full_attr_formula(), id = ~response_id, h0 = 0.5)
  amce_full <- amce(conjoint, full_attr_formula(), id = ~response_id)

  p_mm <- plot_multi_ci(mm_full, h0 = 0.5,
    title = paste0(cfg$label, ": Marginal Means"),
    subtitle = "All attributes | CIs at 90/95/99%",
    show_facets = TRUE)

  p_amce <- plot_multi_ci(amce_full, h0 = 0,
    title = paste0(cfg$label, ": AMCEs"),
    subtitle = "All attributes | CIs at 90/95/99%",
    show_facets = TRUE)

  grid.arrange(p_mm, p_amce, ncol = 2,
    bottom = "Confidence intervals at 99% (thin), 95% (medium), 90% (thick)")
}

# --- H1a: Party detail with labels ---
plot_party_detail <- function(d) {
  conjoint <- d$conjoint
  cfg <- d$cfg

  mm_party <- mm(conjoint, selected ~ PARTY, id = ~response_id, h0 = 0.5)
  amce_party <- amce(conjoint, selected ~ PARTY, id = ~response_id)

  p_mm <- plot_multi_ci(mm_party, h0 = 0.5,
    title = "Party Marginal Means",
    subtitle = "H1a: Far-right stigmatization",
    show_labels = TRUE) +
    labs(x = "MM (Pr of acceptance)")

  p_amce <- plot_multi_ci(amce_party, h0 = 0,
    title = "Party AMCEs",
    subtitle = "Relative to reference category",
    show_labels = TRUE) +
    labs(x = "AMCE")

  grid.arrange(p_mm, p_amce, ncol = 2,
    top = paste0(cfg$label, ": H1a - Party Effects"),
    bottom = "CIs at 99%, 95%, 90%")
}

# --- Subgroup heterogeneity (generic) ---
plot_subgroup_party <- function(d, by_var, by_label, color_vals, h_label) {
  conjoint <- d$conjoint
  cfg <- d$cfg
  by_sym <- rlang::ensym(by_var)

  # Filter to valid subgroup values
  sub_data <- conjoint |> filter(!is.na(!!by_sym))
  groups <- unique(sub_data[[rlang::as_name(by_sym)]])
  if (length(groups) < 2) return(invisible(NULL))

  # Check minimum N per group
  group_ns <- sub_data |> distinct(response_id, !!by_sym) |> count(!!by_sym)
  if (min(group_ns$n) < 30) {
    cat(paste0("Insufficient subgroup N for ", by_label,
               " (min = ", min(group_ns$n), ", need 30)\n\n"))
    return(invisible(NULL))
  }

  # Conditional MMs
  mm_sub <- cj(sub_data, selected ~ PARTY, id = ~response_id,
               estimate = "mm", by = as.formula(paste0("~", rlang::as_name(by_sym))))

  p_mm <- plot_multi_ci(mm_sub, h0 = 0.5,
    title = paste0("Party MMs by ", by_label),
    subtitle = h_label,
    color_var = "BY", color_vals = color_vals) +
    labs(x = "Marginal Mean")

  # mm_diffs
  diff_sub <- mm_diffs(sub_data, selected ~ PARTY, id = ~response_id,
                       by = as.formula(paste0("~", rlang::as_name(by_sym))))
  diff_sub <- add_multi_ci(diff_sub)

  p_diff <- ggplot(diff_sub, aes(y = level)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.4) +
    geom_segment(aes(x = lower99, xend = higher99, y = level, yend = level),
                 color = "grey30", size = 2, alpha = .6) +
    geom_segment(aes(x = lower95, xend = higher95, y = level, yend = level),
                 color = "grey30", size = 3, alpha = .8) +
    geom_segment(aes(x = lower90, xend = higher90, y = level, yend = level),
                 color = "grey30", size = 4, alpha = 1) +
    geom_point(aes(x = estimate, y = level), fill = "white", color = "grey50",
               size = 2.5, pch = 21) +
    geom_label(aes(x = estimate, y = level, label = sprintf("%0.2f", estimate)),
               nudge_y = .25, size = 3, fontface = "bold", alpha = 0.8) +
    labs(title = paste0("Difference (", paste(groups, collapse = " - "), ")"),
         subtitle = "0 = no heterogeneity",
         x = "MM Difference", y = NULL) +
    theme(plot.title = element_text(face = "bold", size = 11),
          plot.subtitle = element_text(size = 9))

  grid.arrange(p_mm, p_diff, ncol = 2,
    top = paste0(cfg$label, ": ", h_label),
    bottom = "CIs at 99%, 95%, 90%")
}

# --- Rejection signal analysis ---
plot_rejection_analysis <- function(d) {
  conjoint <- d$conjoint
  cfg <- d$cfg
  conjoint_nofr <- conjoint |> filter(PARTY != cfg$far_right)

  # Overall rejection effect
  mm_rej <- mm(conjoint_nofr, selected ~ REJECTION_CLEAN, id = ~response_id, h0 = 0.5)

  p_overall <- plot_multi_ci(mm_rej, h0 = 0.5,
    title = "H5: Rejection Signal Effect",
    subtitle = "Non-far-right profiles only",
    show_labels = TRUE) +
    labs(x = "Marginal Mean")

  # Rejection by party
  mm_rej_party <- cj(conjoint_nofr, selected ~ REJECTION_CLEAN, id = ~response_id,
                      estimate = "mm", by = ~PARTY)

  p_party <- plot_multi_ci(mm_rej_party, h0 = 0.5,
    title = "Rejection Signal by Party",
    subtitle = "Effect varies by party?",
    show_facets = TRUE,
    color_var = NULL) +
    labs(x = "Marginal Mean")

  grid.arrange(p_overall, p_party, ncol = 2,
    top = paste0(cfg$label, ": Rejection Signal Deep Dive"),
    bottom = "CIs at 99%, 95%, 90%")
}

# --- Rejection subgroup (H5c, H6) ---
plot_rejection_subgroup <- function(d, by_var, by_label, color_vals, h_label) {
  conjoint_nofr <- d$conjoint |> filter(PARTY != d$cfg$far_right)
  by_sym <- rlang::ensym(by_var)

  sub_data <- conjoint_nofr |> filter(!is.na(!!by_sym))
  groups <- unique(sub_data[[rlang::as_name(by_sym)]])
  if (length(groups) < 2) return(invisible(NULL))

  group_ns <- sub_data |> distinct(response_id, !!by_sym) |> count(!!by_sym)
  if (min(group_ns$n) < 10) {
    cat(paste0("Insufficient subgroup N for ", by_label,
               " (min = ", min(group_ns$n), ")\n\n"))
    return(invisible(NULL))
  }

  mm_sub <- cj(sub_data, selected ~ REJECTION_CLEAN, id = ~response_id,
               estimate = "mm", by = as.formula(paste0("~", rlang::as_name(by_sym))))

  p_mm <- plot_multi_ci(mm_sub, h0 = 0.5,
    title = paste0("Rejection Signal by ", by_label),
    subtitle = h_label,
    color_var = "BY", color_vals = color_vals,
    show_labels = TRUE) +
    labs(x = "Marginal Mean")

  diff_sub <- mm_diffs(sub_data, selected ~ REJECTION_CLEAN, id = ~response_id,
                       by = as.formula(paste0("~", rlang::as_name(by_sym))))
  diff_sub <- add_multi_ci(diff_sub)

  p_diff <- ggplot(diff_sub, aes(y = level)) +
    geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.4) +
    geom_segment(aes(x = lower99, xend = higher99, y = level, yend = level),
                 color = "grey30", size = 2, alpha = .6) +
    geom_segment(aes(x = lower95, xend = higher95, y = level, yend = level),
                 color = "grey30", size = 3, alpha = .8) +
    geom_segment(aes(x = lower90, xend = higher90, y = level, yend = level),
                 color = "grey30", size = 4, alpha = 1) +
    geom_point(aes(x = estimate, y = level), fill = "white", color = "grey50",
               size = 2.5, pch = 21) +
    geom_label(aes(x = estimate, y = level, label = sprintf("%0.2f", estimate)),
               nudge_y = .25, size = 3, fontface = "bold", alpha = 0.8) +
    labs(title = paste0("Difference (", paste(groups, collapse = " - "), ")"),
         x = "MM Difference", y = NULL) +
    theme(plot.title = element_text(face = "bold", size = 11))

  grid.arrange(p_mm, p_diff, ncol = 2,
    top = paste0(d$cfg$label, ": ", h_label),
    bottom = "CIs at 99%, 95%, 90%")
}

# --- PAP contrasts table ---
build_pap_table <- function(d) {
  conjoint <- d$conjoint
  cfg <- d$cfg
  conjoint_nofr <- conjoint |> filter(PARTY != cfg$far_right)
  rows <- list()

  # H1a: Far-right MM vs 0.5
  tryCatch({
    mm_p <- mm(conjoint, selected ~ PARTY, id = ~response_id, h0 = 0.5)
    fr_row <- mm_p |> filter(level == cfg$far_right)
    z <- (fr_row$estimate - 0.5) / fr_row$std.error
    rows$h1a <- tibble(
      Hypothesis = "H1a", Contrast = paste0("MM(", cfg$far_right, ") vs 0.5"),
      Estimate = fr_row$estimate, SE = fr_row$std.error,
      CI_lower = fr_row$lower, CI_upper = fr_row$upper,
      p = 2 * pnorm(-abs(z)))
  }, error = function(e) NULL)

  # H3: mm_diff by ideology for far-right
  tryCatch({
    sub <- conjoint |> filter(!is.na(derecha))
    if (n_distinct(sub$derecha) >= 2) {
      diff_ideo <- mm_diffs(sub, selected ~ PARTY, id = ~response_id, by = ~derecha)
      fr_diff <- diff_ideo |> filter(level == cfg$far_right)
      if (nrow(fr_diff) > 0) {
        z <- fr_diff$estimate[1] / fr_diff$std.error[1]
        rows$h3 <- tibble(
          Hypothesis = "H3", Contrast = paste0("mm_diff(", cfg$far_right, "): Left vs Right"),
          Estimate = fr_diff$estimate[1], SE = fr_diff$std.error[1],
          CI_lower = fr_diff$lower[1], CI_upper = fr_diff$upper[1],
          p = 2 * pnorm(-abs(z)))
      }
    }
  }, error = function(e) NULL)

  # H4.1: mm_diff by gender for far-right
  tryCatch({
    sub <- conjoint |> filter(resp_gender %in% c("Man", "Woman"))
    if (n_distinct(sub$resp_gender) >= 2) {
      diff_gen <- mm_diffs(sub, selected ~ PARTY, id = ~response_id, by = ~resp_gender)
      fr_diff <- diff_gen |> filter(level == cfg$far_right)
      if (nrow(fr_diff) > 0) {
        z <- fr_diff$estimate[1] / fr_diff$std.error[1]
        rows$h41 <- tibble(
          Hypothesis = "H4.1", Contrast = paste0("mm_diff(", cfg$far_right, "): Man vs Woman"),
          Estimate = fr_diff$estimate[1], SE = fr_diff$std.error[1],
          CI_lower = fr_diff$lower[1], CI_upper = fr_diff$upper[1],
          p = 2 * pnorm(-abs(z)))
      }
    }
  }, error = function(e) NULL)

  # H4.2: mm_diff by LGBTQ+ for far-right
  tryCatch({
    if (n_distinct(conjoint$resp_lgbtq) >= 2 && min(table(conjoint$resp_lgbtq)) >= 20) {
      diff_lgbtq <- mm_diffs(conjoint, selected ~ PARTY, id = ~response_id, by = ~resp_lgbtq)
      fr_diff <- diff_lgbtq |> filter(level == cfg$far_right)
      if (nrow(fr_diff) > 0) {
        z <- fr_diff$estimate[1] / fr_diff$std.error[1]
        rows$h42 <- tibble(
          Hypothesis = "H4.2", Contrast = paste0("mm_diff(", cfg$far_right, "): Hetero vs LGBTQ+"),
          Estimate = fr_diff$estimate[1], SE = fr_diff$std.error[1],
          CI_lower = fr_diff$lower[1], CI_upper = fr_diff$upper[1],
          p = 2 * pnorm(-abs(z)))
      }
    }
  }, error = function(e) NULL)

  # H5: Rejection signal difference
  tryCatch({
    mm_rej <- mm(conjoint_nofr, selected ~ REJECTION_CLEAN, id = ~response_id, h0 = 0.5)
    with_sig <- mm_rej |> filter(level == "With rejection signal")
    without_sig <- mm_rej |> filter(level == "Without rejection signal")
    if (nrow(with_sig) > 0 && nrow(without_sig) > 0) {
      diff_est <- with_sig$estimate - without_sig$estimate
      diff_se <- sqrt(with_sig$std.error^2 + without_sig$std.error^2)
      z <- diff_est / diff_se
      rows$h5 <- tibble(
        Hypothesis = "H5", Contrast = "MM(with signal) - MM(without signal)",
        Estimate = diff_est, SE = diff_se,
        CI_lower = diff_est - 1.96 * diff_se, CI_upper = diff_est + 1.96 * diff_se,
        p = 2 * pnorm(-abs(z)))
    }
  }, error = function(e) NULL)

  # H5c: mm_diff rejection by ideology
  tryCatch({
    sub <- conjoint_nofr |> filter(!is.na(derecha))
    if (n_distinct(sub$derecha) >= 2) {
      diff_rej_ideo <- mm_diffs(sub, selected ~ REJECTION_CLEAN, id = ~response_id, by = ~derecha)
      sig_row <- diff_rej_ideo |> filter(level == "With rejection signal")
      if (nrow(sig_row) > 0) {
        z <- sig_row$estimate[1] / sig_row$std.error[1]
        rows$h5c <- tibble(
          Hypothesis = "H5c", Contrast = "mm_diff(rejection signal): Left vs Right",
          Estimate = sig_row$estimate[1], SE = sig_row$std.error[1],
          CI_lower = sig_row$lower[1], CI_upper = sig_row$upper[1],
          p = 2 * pnorm(-abs(z)))
      }
    }
  }, error = function(e) NULL)

  # H6: mm_diff rejection by far-right support
  tryCatch({
    if (n_distinct(conjoint_nofr$resp_farright) >= 2 &&
        min(table(conjoint_nofr$resp_farright)) >= 10) {
      diff_rej_fr <- mm_diffs(conjoint_nofr, selected ~ REJECTION_CLEAN,
                               id = ~response_id, by = ~resp_farright)
      sig_row <- diff_rej_fr |> filter(level == "With rejection signal")
      if (nrow(sig_row) > 0) {
        z <- sig_row$estimate[1] / sig_row$std.error[1]
        rows$h6 <- tibble(
          Hypothesis = "H6", Contrast = "mm_diff(rejection signal): FR supp vs not",
          Estimate = sig_row$estimate[1], SE = sig_row$std.error[1],
          CI_lower = sig_row$lower[1], CI_upper = sig_row$upper[1],
          p = 2 * pnorm(-abs(z)))
      }
    }
  }, error = function(e) NULL)

  tbl_data <- bind_rows(rows) |>
    mutate(
      Estimate = round(Estimate, 3),
      SE = round(SE, 3),
      CI = paste0("[", round(CI_lower, 3), ", ", round(CI_upper, 3), "]"),
      p = round(p, 4),
      Sig = case_when(p < .01 ~ "***", p < .05 ~ "**", p < .10 ~ "*", TRUE ~ "")
    ) |>
    select(Hypothesis, Contrast, Estimate, SE, CI, p, Sig)

  sig_rows <- which(tbl_data$p < 0.05)
  marg_rows <- which(tbl_data$p >= 0.05 & tbl_data$p < 0.10)

  tbl <- tbl_data |>
    gt() |>
    tab_header(title = paste0(d$cfg$label, ": PAP Contrasts Summary"),
               subtitle = paste0("N = ", nrow(d$respondents), " respondents"))

  if (length(sig_rows) > 0) {
    tbl <- tbl |> tab_style(style = cell_fill(color = "#d4edda"),
                             locations = cells_body(rows = sig_rows))
  }
  if (length(marg_rows) > 0) {
    tbl <- tbl |> tab_style(style = cell_fill(color = "#fff3cd"),
                             locations = cells_body(rows = marg_rows))
  }
  tbl
}
```

## 6.1 Full Attribute Overview {.tabset}

::: {.panel-tabset}

### Germany

```{r fullattr-germany, eval=show_results, fig.height=14, fig.width=12}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(plot_full_attributes(data[["germany"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

### Austria

```{r fullattr-austria, eval=show_results, fig.height=14, fig.width=12}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(plot_full_attributes(data[["austria"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

:::

## 6.2 H1a: Far-Right Stigma {.tabset}

::: {.panel-tabset}

### Germany

```{r h1a-germany, eval=show_results, fig.height=6, fig.width=12}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(plot_party_detail(data[["germany"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

### Austria

```{r h1a-austria, eval=show_results, fig.height=6, fig.width=12}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(plot_party_detail(data[["austria"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

:::

## 6.3 Subgroup Heterogeneity {.tabset}

::: {.panel-tabset}

### Germany

```{r subgroup-germany, eval=show_results, fig.height=7, fig.width=14}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  d <- data[["germany"]]
  tryCatch(print(plot_subgroup_party(d, derecha, "Ideology",
    c("#E74C3C", "#3498DB"), "H3: Right-wing evaluate far-right more positively")),
    error = function(e) cat(paste0("H3 Error: ", e$message, "\n\n")))
}
```

```{r subgroup-gender-germany, eval=show_results, fig.height=7, fig.width=14}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  d <- data[["germany"]]
  tryCatch(print(plot_subgroup_party(d, resp_gender, "Gender",
    c("#3498DB", "#E74C3C"), "H4.1: Women penalize far-right more")),
    error = function(e) cat(paste0("H4.1 Error: ", e$message, "\n\n")))
}
```

```{r subgroup-lgbtq-germany, eval=show_results, fig.height=7, fig.width=14}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  d <- data[["germany"]]
  tryCatch(print(plot_subgroup_party(d, resp_lgbtq, "LGBTQ+ Status",
    c("#2ECC71", "#9B59B6"), "H4.2: LGBTQ+ penalize far-right more")),
    error = function(e) cat(paste0("H4.2 Error: ", e$message, "\n\n")))
}
```

### Austria

```{r subgroup-austria, eval=show_results, fig.height=7, fig.width=14}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  d <- data[["austria"]]
  tryCatch(print(plot_subgroup_party(d, derecha, "Ideology",
    c("#E74C3C", "#3498DB"), "H3: Right-wing evaluate far-right more positively")),
    error = function(e) cat(paste0("H3 Error: ", e$message, "\n\n")))
}
```

```{r subgroup-gender-austria, eval=show_results, fig.height=7, fig.width=14}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  d <- data[["austria"]]
  tryCatch(print(plot_subgroup_party(d, resp_gender, "Gender",
    c("#3498DB", "#E74C3C"), "H4.1: Women penalize far-right more")),
    error = function(e) cat(paste0("H4.1 Error: ", e$message, "\n\n")))
}
```

```{r subgroup-lgbtq-austria, eval=show_results, fig.height=7, fig.width=14}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  d <- data[["austria"]]
  tryCatch(print(plot_subgroup_party(d, resp_lgbtq, "LGBTQ+ Status",
    c("#2ECC71", "#9B59B6"), "H4.2: LGBTQ+ penalize far-right more")),
    error = function(e) cat(paste0("H4.2 Error: ", e$message, "\n\n")))
}
```

:::

## 6.4 Rejection Signal (H5, H5c, H6) {.tabset}

::: {.panel-tabset}

### Germany

```{r rejection-germany, eval=show_results, fig.height=8, fig.width=12}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_analysis(data[["germany"]])),
           error = function(e) cat(paste0("H5 Error: ", e$message, "\n\n")))
}
```

```{r rejection-h5c-germany, eval=show_results, fig.height=6, fig.width=12}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_subgroup(data[["germany"]], derecha, "Ideology",
    c("#E74C3C", "#3498DB"), "H5c: Rejection signal premium larger among left-leaning")),
    error = function(e) cat(paste0("H5c Error: ", e$message, "\n\n")))
}
```

```{r rejection-h6-germany, eval=show_results, fig.height=6, fig.width=12}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_subgroup(data[["germany"]], resp_farright, "Far-Right Support",
    c("#E67E22", "#7F8C8D"), "H6: Far-right supporters reject anti-far-right signals")),
    error = function(e) cat(paste0("H6 Error: ", e$message, "\n\n")))
}
```

### Austria

```{r rejection-austria, eval=show_results, fig.height=8, fig.width=12}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_analysis(data[["austria"]])),
           error = function(e) cat(paste0("H5 Error: ", e$message, "\n\n")))
}
```

```{r rejection-h5c-austria, eval=show_results, fig.height=6, fig.width=12}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_subgroup(data[["austria"]], derecha, "Ideology",
    c("#E74C3C", "#3498DB"), "H5c: Rejection signal premium larger among left-leaning")),
    error = function(e) cat(paste0("H5c Error: ", e$message, "\n\n")))
}
```

```{r rejection-h6-austria, eval=show_results, fig.height=6, fig.width=12}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(print(plot_rejection_subgroup(data[["austria"]], resp_farright, "Far-Right Support",
    c("#E67E22", "#7F8C8D"), "H6: Far-right supporters reject anti-far-right signals")),
    error = function(e) cat(paste0("H6 Error: ", e$message, "\n\n")))
}
```

:::

## 6.5 PAP Contrasts Summary {.tabset}

::: {.panel-tabset}

### Germany

```{r pap-germany, eval=show_results}
if ("germany" %in% names(data) && nrow(data[["germany"]]$respondents) >= min_n) {
  tryCatch(build_pap_table(data[["germany"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

### Austria

```{r pap-austria, eval=show_results}
if ("austria" %in% names(data) && nrow(data[["austria"]]$respondents) >= min_n) {
  tryCatch(build_pap_table(data[["austria"]]),
           error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
}
```

:::

## 6.6 Country Comparison

```{r country-comparison-v2, eval=show_results, fig.height=8, fig.width=12}
if (length(data) == 2) {
  pooled <- map_dfr(names(data), function(ck) {
    d <- data[[ck]]
    d$conjoint |>
      mutate(
        PARTY_HARMONIZED = case_when(
          PARTY == d$cfg$far_right ~ "Far-right",
          PARTY == d$cfg$center_right ~ "Center-right",
          TRUE ~ "Other"
        ),
        country = d$cfg$label
      ) |>
      select(response_id, round, selected, PARTY_HARMONIZED, country)
  }) |>
    mutate(
      PARTY_HARMONIZED = factor(PARTY_HARMONIZED,
                                levels = c("Center-right", "Other", "Far-right")),
      country = factor(country)
    )

  if (nrow(pooled) > 0) {
    tryCatch({
      mm_country <- cj(pooled, selected ~ PARTY_HARMONIZED, id = ~response_id,
                        estimate = "mm", by = ~country) |>
        add_multi_ci()

      p <- plot_multi_ci(mm_country, h0 = 0.5,
        title = "Country Comparison: Party MMs (Harmonized)",
        subtitle = "H1a: Far-right penalty stronger in Germany than Austria?",
        color_var = "BY",
        color_vals = c("#DD1100", "#2E86C1"),
        show_labels = TRUE) +
        labs(x = "Marginal Mean")
      print(p)
    }, error = function(e) cat(paste0("Error: ", e$message, "\n\n")))
  }
}
```


# 7. Attention Check {.tabset}

```{r attn-helpers}
plot_attention_check <- function(d, country_label) {
  raw <- d$raw
  attn_col <- "feeling_thermometer_9"

  if (!attn_col %in% names(raw)) {
    cat("No attention check data yet.\n\n")
    return(invisible(NULL))
  }

  attn_vals <- raw |>
    filter(!is.na(.data[[attn_col]])) |>
    mutate(value = suppressWarnings(as.numeric(.data[[attn_col]]))) |>
    filter(!is.na(value))

  if (nrow(attn_vals) == 0) {
    cat("No attention check data yet.\n\n")
    return(invisible(NULL))
  }

  n_total <- nrow(attn_vals)
  n_pass <- sum(attn_vals$value == 3)
  n_fail <- n_total - n_pass
  fail_pct <- round(n_fail / n_total * 100, 1)

  # Bar chart of responses
  response_counts <- attn_vals |>
    count(value) |>
    mutate(
      pass = ifelse(value == 3, "Pass (correct = 3)", "Fail"),
      pct = n / sum(n) * 100,
      label = paste0(n, " (", round(pct, 1), "%)")
    )

  p <- ggplot(response_counts, aes(x = factor(value), y = n, fill = pass)) +
    geom_col(color = "white", width = 0.7) +
    geom_text(aes(label = label), vjust = -0.3, size = 3.5, fontface = "bold") +
    scale_fill_manual(values = c("Pass (correct = 3)" = "#27AE60", "Fail" = "#E74C3C")) +
    scale_x_discrete(labels = 0:10) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
    labs(
      title = paste0(country_label, ": Attention Check (Feeling Thermometer)"),
      subtitle = paste0(n_pass, "/", n_total, " passed | ",
                        n_fail, " failed (", fail_pct, "% failure rate)"),
      x = "Response value (correct answer = 3)", y = "Count", fill = NULL
    ) +
    theme(
      plot.title = element_text(face = "bold"),
      legend.position = "bottom"
    )

  print(p)
}
```

::: {.panel-tabset}

## Germany

```{r attn-germany, fig.height=5}
if ("germany" %in% names(data)) {
  plot_attention_check(data[["germany"]], "Germany")
}
```

## Austria

```{r attn-austria, fig.height=5}
if ("austria" %in% names(data)) {
  plot_attention_check(data[["austria"]], "Austria")
}
```

:::


# 8. Traffic-Light Summary

```{r summary-dashboard}
build_status <- function(d) {
  cfg <- d$cfg
  conjoint <- d$conjoint
  n_resp <- nrow(d$respondents)
  n_profiles <- nrow(conjoint)

  checks <- list()

  # Collection progress
  pct_complete <- n_resp / cfg$target_n * 100
  checks$collection <- tibble(
    Check = paste0("Collection (", cfg$label, ")"),
    Status = case_when(pct_complete >= 80 ~ "GREEN",
                       pct_complete >= 50 ~ "YELLOW",
                       TRUE ~ "RED"),
    Details = paste0(n_resp, "/", cfg$target_n, " (", round(pct_complete, 1), "%)")
  )

  # Quota deviations
  quota_results <- check_quotas(d)
  max_dev <- max(abs(quota_results$deviation), na.rm = TRUE)
  checks$quotas <- tibble(
    Check = paste0("Quotas (", cfg$label, ")"),
    Status = case_when(max_dev <= 3 ~ "GREEN",
                       max_dev <= 5 ~ "YELLOW",
                       TRUE ~ "RED"),
    Details = paste0("Max deviation: ", round(max_dev, 1), "pp")
  )

  # Party randomization
  party_dist <- conjoint |> filter(!is.na(PARTY)) |> count(PARTY)
  party_p <- chisq.test(party_dist$n, p = rep(1/length(cfg$parties),
                                               length(cfg$parties)))$p.value
  checks$party <- tibble(
    Check = paste0("Party randomization (", cfg$label, ")"),
    Status = ifelse(party_p > 0.05, "GREEN", ifelse(party_p > 0.01, "YELLOW", "RED")),
    Details = paste0("chi-sq p=", round(party_p, 3))
  )

  # Rejection signal
  non_fr <- conjoint |> filter(PARTY != cfg$far_right)
  rej_rate <- mean(non_fr$REJECTION_BINARY, na.rm = TRUE)
  checks$rejection <- tibble(
    Check = paste0("Rejection rate (", cfg$label, ")"),
    Status = case_when(abs(rej_rate - 0.3) <= 0.05 ~ "GREEN",
                       abs(rej_rate - 0.3) <= 0.10 ~ "YELLOW",
                       TRUE ~ "RED"),
    Details = paste0(round(rej_rate * 100, 1), "% (target: 30%)")
  )

  # Face deduplication
  face_fails <- d$conjoint |>
    group_by(response_id) |>
    summarise(has_repeat = n() > n_distinct(person), .groups = "drop") |>
    filter(has_repeat)
  checks$faces <- tibble(
    Check = paste0("Face dedup (", cfg$label, ")"),
    Status = ifelse(nrow(face_fails) == 0, "GREEN", "RED"),
    Details = paste0(nrow(face_fails), " failures")
  )

  # Speeders
  durations <- d$respondents |>
    mutate(duration_min = as.numeric(duration_seconds) / 60) |>
    filter(!is.na(duration_min))
  speeder_pct <- mean(durations$duration_min < 5, na.rm = TRUE) * 100
  checks$speeders <- tibble(
    Check = paste0("Speeders (", cfg$label, ")"),
    Status = case_when(speeder_pct <= 5 ~ "GREEN",
                       speeder_pct <= 10 ~ "YELLOW",
                       TRUE ~ "RED"),
    Details = paste0(round(speeder_pct, 1), "%")
  )

  # Attention check
  attn_col <- "feeling_thermometer_9"
  if (attn_col %in% names(d$raw)) {
    attn_vals <- suppressWarnings(as.numeric(d$raw[[attn_col]]))
    attn_vals <- attn_vals[!is.na(attn_vals)]
    if (length(attn_vals) > 0) {
      attn_fail_pct <- mean(attn_vals != 3) * 100
      checks$attention <- tibble(
        Check = paste0("Attention check (", cfg$label, ")"),
        Status = case_when(attn_fail_pct <= 5 ~ "GREEN",
                           attn_fail_pct <= 15 ~ "YELLOW",
                           TRUE ~ "RED"),
        Details = paste0(round(attn_fail_pct, 1), "% failed")
      )
    }
  }

  bind_rows(checks)
}

all_status <- map_dfr(names(data), function(ck) build_status(data[[ck]]))

green_rows <- which(all_status$Status == "GREEN")
yellow_rows <- which(all_status$Status == "YELLOW")
red_rows <- which(all_status$Status == "RED")

tbl <- all_status |>
  gt() |>
  tab_header(title = "Fieldwork Status Dashboard",
             subtitle = paste0("Last updated: ", Sys.time()))

if (length(green_rows) > 0) {
  tbl <- tbl |> tab_style(style = cell_fill(color = "#d4edda"),
                           locations = cells_body(rows = green_rows))
}
if (length(yellow_rows) > 0) {
  tbl <- tbl |> tab_style(style = cell_fill(color = "#fff3cd"),
                           locations = cells_body(rows = yellow_rows))
}
if (length(red_rows) > 0) {
  tbl <- tbl |> tab_style(style = cell_fill(color = "#f8d7da"),
                           locations = cells_body(rows = red_rows))
}
tbl
```

---

*Generated by fieldwork_monitor.qmd | Last rendered: `r Sys.time()`*
